---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    latex_engine: pdflatex
    template: C:/Users/bomim/Documents/cryingdoves/paper/svm-latex-ms2.tex
title: "Does Cooperation with Neighboring Countries Matter?
The Dynamics of External Relations and Approval Ratings in Japan and South Korea"

thanks: "The paper's revision history and the materials needed to reproduce its analyses can be found [on Github here](http://github.com/bomibonnie/cryingdoves). Corresponding author: [bomi-lee-1@uiowa.edu](mailto:bomi-lee-1@uiowa.edu). Current version: `r format(Sys.time(), '%B %d, %Y')`."
author:
- name: Bomi Lee
  affiliation: University of Iowa
abstract: "In general, international issues are less salient than domestic issues to the public, but the diversionary theory and the rally-’round-the-flag effect explain that some types of conflictual external events can be salient enough to capture the public’s attention, which leads to the public’s support for the leaders. Although the conflictual external events are the part of a relationship, those are not equal to the relationship. In this context, I examine the effect of net cooperation on approval ratings considering all types of events from the most conflictual events to the most cooperative events. The event data are drawn from the Temporally Extended, Regular, Reproducible International Event Records (TERRIER) Project and each event is weighted by the Goldstein score. As for the approval ratings, I focus on the Japanese cabinet approval ratings from February 1986 to July 2017, and the South Korean presidential approval ratings from March 1993 to December 2014. Since there could be an endogeneity problem, I conduct the Granger Causality test and IRFs using a VAR model, and set a single equation based on the result. Considering the dynamics within the variables, I use an autoregressive distributed lag (ADL) model including the lagged values of the variables. The result shows that the net cooperation of Japan-China negatively affect the Japanese approval ratings, and that of South Korea-Japan also negatively influence the South Korean approval ratings."
keywords: ", always seem silly, to me, given google, but regardless"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: single
bibliography: \dummy{`r file.path(getwd(), 'cryingdoves')`}
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# load all the packages you will use below 
library(dotwhisker)
library(tidyverse)
```

# Introduction 

Does cooperative behavior toward neighboring countries affect domestic politics? Actually, many scholars focus on the effect of conflictual event on domestic politics. For example, diversionary theory explains that leaders are more likely to use force against other countries when they have domestic turmoil such as low economic growth. The point is that when a state has external conflict the leaders can get a better position in the domestic politics by distracting the public’s attention from domestic issues toward external conflict. Similarly, the rally-’round-the-flag effect focuses on the public’s tendency to support its government when it has an external threat. For instance, in July 2017, the lowest Japanese cabinet’s approval rating was reported in the Yomiuri Shimbun, 36%.^[Yomiuri poll was conducted on 7-9 July. More details can be seen on the following link (http://www.yomiuri.co.jp/election/poll/20170710-OYT8T50024.html).] The reason for the rapid decrease in the approval rating is the Japanese prime minister, Shinzo Abe’s domestic scandals. Even though his efforts to end the scandals were not successful, his cabinet approval rating recovered the following month because of North Korea’s series of missile tests and China’s assertive attitude in the East China Sea. The rally effect is not limited to the severe threat. When the former Korean President, Lee Myung-bak, visited a disputed island between South Korea and Japan in 2012, his approval ratings increased about 9 percent [@Gallup2012]. 



```{r mtcars}
summary(mtcars)
```

---
# This is a comment, set off with --- and started with #.  Comments are good for notes to self that you don't want to show up in the output.  Below is LaTeX code for a page break.
---
\pagebreak 
## Including Plots

You can also embed plots, for example:

```{r dotwhisker_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:dotwhisker_plot}Dot-and-Whisker Plot Example"}
m1 <- lm(mpg ~ wt + cyl + disp + gear, data = mtcars)
m2 <- update(m1, . ~ . + hp) # add another predictor
m3 <- update(m2, . ~ . + am) # and another 

dwplot(list(m1, m2, m3),
       vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2)) %>% # plot line at zero _behind_ coefs
    relabel_predictors(c(wt = "Weight",                       
                         cyl = "Cylinders", 
                         disp = "Displacement", 
                         hp = "Horsepower", 
                         gear = "Gears", 
                         am = "Manual")) +
     theme_bw() + xlab("Coefficient Estimate") + ylab("") +
     geom_vline(xintercept = 0, colour = "grey60", linetype = 2) +
     ggtitle("Predicting Gas Mileage") +
     theme(plot.title = element_text(face="bold"),
           legend.position = c(0.007, 0.01),
           legend.justification = c(0, 0), 
           legend.background = element_rect(colour="grey80"),
           legend.title = element_blank()) 
```

Figure \ref{fig:dotwhisker_plot} is a plot made in the \texttt{dotwhisker} package [@Solt2015c]. Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Citations
Want to cite something?

1. Find your cite key in your bib file.
1. Put an @ before it, like @Solt2017, or whatever it is
1. @Solt2017 creates an in-text citation
1. [@Herndon2014] creates a parenthetical citation

As @Gelman2014 note, the garden of forking paths can pose problems for researchers even when they are acting in good faith.

## Other Common Things

> This will create a block quote, if you want one.

Dropping a footnote is easy.^[See? Not hard at all.]

